rotation_runs2019

### 2019-10-10 inst/documents/rotation_runs2019.Rmd
dispersal modified and seemingly working

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=5.4, comment=NA, results='asis'}

@@

# now specify an experiment from the multi-experiment file
#id_expt <- 'A2'
#id_expt <- 'A4'
id_expt <- 'B2'

@@

    #code to rerun approx this scenario, can be copied from pdf and pasted into R
    #has to cope with converting vectors to strings
    #spaces between args stop the pdf from messing with words
    cat(paste0("run_rot(n_insecticides=",linputs$n_insecticides,", ",
                "rot_interval=",linputs$rot_interval,", ",
                #"mort_or_freq='",linputs$mort_or_freq,"', ", #quotes dont work, freq is now default
                #'mort_or_freq="',linputs$mort_or_freq,'", ',
                "start_freqs=",signif(linputs$start_freqs,2),", ", 
                "cost=c(",paste(signif(linputs$cost,2),collapse=','),"), ", 
                "eff=c(",paste(signif(linputs$eff,2),collapse=','),"), ",               
                "dom_sel=c(",paste(signif(linputs$dom_sel,2),collapse=','),"), ",
                "dom_cos=c(",paste(signif(linputs$dom_cos,2),collapse=','),"), ",
                "rr=c(",paste(signif(linputs$rr,2),collapse=','),"), ",
                "expo_hi=",signif(linputs$expo_hi,2),", ",
                "coverage=",signif(linputs$coverage,2),", ",
                "migration=",signif(linputs$migration,2),", ",
                #"max_gen=",linputs$max_gen,", ", 
                "min_rwr_interval=",linputs$min_rwr_interval,            
                ")\n\n") )

>>>>

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=5.2, comment=NA, results='asis'}

@@

# now specify an experiment from the multi-experiment file
#id_expt <- 'A2'
#id_expt <- 'A3'
#id_expt <- 'A4'
#id_expt <- 'B2'
#id_expt <- 'B3'
id_expt <- 'B4'

@@

    #code to rerun approx this scenario, can be copied from pdf and pasted into R
    #has to cope with converting vectors to strings
    #spaces between args stop the pdf from messing with words
    cat(paste0( "run_rot(rot_interval=",linputs$rot_interval,", ", 
                "n_insecticides=",linputs$n_insecticides,", ",
                #"mort_or_freq='",linputs$mort_or_freq,"', ", #quotes dont work, freq is now default
                #'mort_or_freq="',linputs$mort_or_freq,'", ',
                "start_freqs=",signif(linputs$start_freqs,2),", ", 
                "cost=c(",paste(signif(linputs$cost,2),collapse=','),"), ", 
                "eff=c(",paste(signif(linputs$eff,2),collapse=','),"), ",               
                "dom_sel=c(",paste(signif(linputs$dom_sel,2),collapse=','),"), ",
                "dom_cos=c(",paste(signif(linputs$dom_cos,2),collapse=','),"), ",
                "rr=c(",paste(signif(linputs$rr,2),collapse=','),"), ",
                "expo_hi=",signif(linputs$expo_hi,2),", ",
                "male_expo_prop=",signif(linputs$male_expo_prop,2),", ",
                "coverage=",signif(linputs$coverage,2),", ",
                "migration=",signif(linputs$migration,2),", ",
                #"max_gen=",linputs$max_gen,", ", 
                "min_rwr_interval=",linputs$min_rwr_interval,            
                ")\n\n") )

### 2019-10-10 inst/documents/rotations_notes.Rmd
dispersal modified and seemingly working

# 9/10/19

spent the day sweating over getting migration working.

@@

@@

RAF <- set_start_freqs(n=3, freqs=1)
> RAF1gen <- RAF[,,,1] # to view generation 1
> #set freqs in refugia to 0
> RAF1gen[,,'refugia']  <- 0
> #testing migration
> RAF2 <- rot_migrate(RAF1gen, migration=0.5, coverage=0.5, verbose=TRUE)
  m.intervention f.intervention m.refugia f.refugia
1              1              1         0         0
2              1              1         0         0
3              1              1         0         0
  m.intervention f.intervention m.refugia f.refugia
1           0.75           0.75      0.25      0.25
2           0.75           0.75      0.25      0.25
3           0.75           0.75      0.25      0.25

> RAF2 <- rot_migrate(RAF1gen, migration=1, coverage=0.1, verbose=TRUE)
  m.intervention f.intervention m.refugia f.refugia
1              1              1         0         0
2              1              1         0         0
3              1              1         0         0
  m.intervention f.intervention m.refugia f.refugia
1            0.1            0.1       0.1       0.1
2            0.1            0.1       0.1       0.1
3            0.1            0.1       0.1       0.1

@@

~ maybe have a set_raf() function too

>>>>

# 9/10/19
spent the day sweating over getting migration working.

@@

# 10/10/9
migration effects on gens under thresh
run_rot(coverage=0.5, cost=0, migration=0) #64
run_rot(coverage=0.5, cost=0, migration=0.01) #72
run_rot(coverage=0.5, cost=0, migration=0.1) #92
run_rot(coverage=0.5, cost=0, migration=0.3) #104
run_rot(coverage=0.5, cost=0, migration=0.6) #116
run_rot(coverage=0.5, cost=0, migration=0.8) #120
run_rot(coverage=0.5, cost=0, migration=1) #124

migration limits ? 0.01 - 0.6

But other A3 scenarios showe that nearly all runs with migration > 0.2 or 0.3 have treated area & refugia with very similar frequency curves.

I noticed that male_expo_prop min was 1 in earlier runs, changed to 0

@@

@@
